---
# title: 

output: github_document
fig_caption: yes


---
\     


### **Details on Bayesian Lasso implementation**     
We implemented the Bayesian Lasso procedure for coefficients on the block-level portion of the model, with specific variables depending on which model type was being estimated. Similar to Gerber et al. [-@gerber2015] and Stevens and Conway [-@Stevens2019], we searched over 50 potential values of prior variance for the Laplace distribution ranging from 0.1--5 on the log scale, which translated to ~1.1--148 when transformed. We selected the optimal prior for each model type at each scale by comparing models using Watanabe-Akaike Information Criterion [WAIC, @watanabe2010].  

\  
  
For this demonstration, we will limit the lasso implementation to 10 values of the prior variance, as the models are run separately for each value of the variance. For simplicity, we will use total human footprint as the only block-level covariate. In the full analysis, these models were run in parallel on a high performance computing system (Digital Research Alliance of Canada, formerly Compute Canada). 


```{r, eval = F, message = F, warning = F}
# Load the libraries 
library(jagsUI)
library(loo) 

# Load the data
load("docs/lasso_data.Rdata")

block.cov <- data.frame(total.hf = rowSums(block_cov.test))

# Create the block-level model matrix
cov.block <- model.matrix(~ ., data = data.frame(block.cov))

# Create teh point-level model matrix, with forest age scaled 
pt.cov <- data.frame(age = scale(pt_cov.test$age), pt_cov.test[, grep("dom", colnames(pt_cov.test))])
cov.point <- model.matrix(~ as.matrix(pt.cov))

# Create the array of detection covariates
cov.p <- det_cov.test[, , 1:3] 

# Set the lambda values for lasso testing
nlam <- 10
log.lambda=seq(0.1, 5, length = nlam)
lambda <- exp(log.lambda)


```

First, run a single model with the lowest lambda value
```{r, eval = F, message = F, warning = F}
scale <- 2
ni <- 1000
nb <- 500
nt <- 1
nc <- 3


mod.lam <- lambda[i]  # The lambda value to use


params_1 <- c("beta.block", "beta.point", "beta.p", "l.score", "lprob.y")
zst <- apply(spp.test[, -1], 1, function(x) max(x, na.rm = T))  
zbst <- rep(1, nrow(cov.point))

inits <- function() {list(zp = zst, zb = zbst, beta.block = rnorm(ncol(cov.block)), beta.point = rnorm(ncol(cov.point)), beta.p = rnorm(dim(cov.p)[3]))}    

data <- list(y = spp.test[, -1], cov.p = cov.p, cov.point = cov.point, cov.block = cov.block, n.surv = nsurv.test$nsurv, n.site = nrow(spp.test), n.block = nrow(cov.block), n.beta.block = ncol(cov.block), n.beta.point = ncol(cov.point), n.beta.p = dim(cov.p)[3], n.scale = scale^2, block = as.numeric(as.factor(block.test$blockID)), point.block = as.numeric(as.factor(pt_cov.test$block)), indicator = zst, lambda = mod.lam)

system.time({
  out <- jags(data = data, inits = inits, parameters.to.save =  params_1, 
              model.file =  "block_occupancy_lasso.txt", n.chains = nc, n.thin = nt, 
              n.iter = ni, n.burnin = nb, parallel = TRUE)
})


```

Next, put it into a loop and save the log scores to find the lambda values that best fit the data 

```{r, eval = F, message = F, warning = F}
lasso_scores <- lapply(1:length(lambda), function(i){
  mod.lam <- lambda[i]  # The lambda value to use
  
  
  params_1 <- c("beta.block", "beta.point", "beta.p", "l.score", "lprob.y")
  zst <- apply(spp.test[, -1], 1, function(x) max(x, na.rm = T))  
  zbst <- rep(1, nrow(cov.point))
  
  inits <- function() {list(zp = zst, zb = zbst, beta.block = rnorm(ncol(cov.block)), beta.point = rnorm(ncol(cov.point)), beta.p = rnorm(dim(cov.p)[3]))}    
  
  data <- list(y = spp.test[, -1], cov.p = cov.p, cov.point = cov.point, cov.block = cov.block, n.surv = nsurv.test$nsurv, n.site = nrow(spp.test), n.block = nrow(cov.block), n.beta.block = ncol(cov.block), n.beta.point = ncol(cov.point), n.beta.p = dim(cov.p)[3], n.scale = scale^2, block = as.numeric(as.factor(block.test$blockID)), point.block = as.numeric(as.factor(pt_cov.test$block)), indicator = zst, lambda = mod.lam)
  
  system.time({
    out <- jags(data = data, inits = inits, parameters.to.save =  params_1, 
                model.file =  "block_occupancy_lasso.txt", n.chains = nc, n.thin = nt, 
                n.iter = ni, n.burnin = nb, parallel = TRUE)
  })
  
  Rhats <- out$Rhat$beta.block
  log.score <- out$mean$l.score
  waic <- waic(out$sims.list$lprob.y)
  
  return(list(waic = waic$estimates[3, 1], log.score = log.score, Rhats = Rhats))
  
})




```



