---
title: "Running a scale-integrated occupancy model with Bayesian lasso for variable selection."
author: "Andrew D. Crosby"
site: bookdown::bookdown_site
output: 
  md_document:
    variant: gfm
    toc: FALSE
    toc_depth: 2
    number_sections: FALSE
bibliography: docs/scale-integration-library.json
citation-style: docs/landscape-ecology.csl

link-citations: true
github-repo: https://github.com/crosbya1/scale-integrated-occupancy.git
description: "Description and code for running a scale-integrated occupancy model with Bayesian Lasso for variable selection"
---

```{r GlobalOptions, echo=FALSE}
options(bookdown.render.file_scope = FALSE, knitr.duplicate.label = "allow") 
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r setup, include=FALSE, cache=FALSE}
#Set root directory to R project root
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r echo=FALSE, out.width = '100%'}
library(kableExtra)
library(knitr)
```

# Appendix B: Running a scale-integrated occupancy model with Bayesian lasso for variable selection  

Supporting information for:   
Domains of scale in cumulative effects of energy sector development on boreal birds  

Andrew D. Crosby, Lionel Leston, Erin M. Bayne, Péter Sólymos, C. Lisa Mahon, Judith D. Toms, Teegan D.S. Docherty, Samantha J. Song   


## Overview
```{r child = 'docs/R/01_overview.Rmd'}
```


## Importing and processing the Big Grid data 
```{r child = 'docs/R/data-processing.Rmd'}
```

## Description of model code 
```{r child = 'docs/R/hierarchical-model-code.Rmd'}
```

## Bayesian Lasso implementation 
```{r child = 'docs/R/lasso-implementation.Rmd'}
```

## References


<div id="refs"></div>



